---
title: "R course assessment Mandukhai"
author: "Mandukhai Ganbat"
date: "`r date()`"
format:
  html:
    toc: true
    code-fold: show
    code-tools: true
    df-print: paged
    embed-resources: true
  pdf:
    toc: true
  docx:
    toc: true
---

```{r}
#| output: false
# Load libraries

library(survival)
library(survminer)
```

## Introduction

The aim of this final assignment is to generate Kaplan-Meier curve for lung cancer survival rates stratified by gender.

## Data

I have obtained and processed the lung cancer survival data from R's built-in database, "survival".

```{r}
#| output: false

source("C:/Users/mg23g383/Desktop/R course tutorial/project-template-main/my_R_course_day1/Git/Rcoursefinal/R/01_final_kaplanmeier.R")
```

@fig-cases illustrates the number at risk by gender in lung cancer survival. This information holds clinical significance (p = 0.0049), indicating a notable association between gender and lung cancer survival rates. Furthermore, the observed trend suggests that lung cancer survival decreases over time.

```{r}
#| label: fig-cases
survivalplot
```

## Conclusions

The observed trend indicates a decrease in lung cancer survival over time. These findings underscore the importance of further research and targeted interventions to address disparities in lung cancer outcomes based on gender.

<!-- ```{r} -->

<!-- # Process data -->

<!-- region <- "CH" -->

<!-- window_start <- ymd("2020-09-01") -->

<!-- window_end <- ymd("2020-11-30") -->

<!-- cases <- cases |> -->

<!--   filter(geoRegion == region & datum >= window_start & datum <= window_end) |> -->

<!--   select(datum, entries) -->

<!-- cases -->

<!-- ``` -->

<!-- ```{r} -->

<!-- #| label: fig-cases -->

<!-- #| fig-cap: "Laboratory-confirmed cases of COVID-19 in Switzerland in 2020." -->

<!-- #| fig-width: 8 -->

<!-- #| fig-height: 4 -->

<!-- ggplot(cases, aes(x = datum, y = entries)) + -->

<!--   geom_bar(stat = "identity", fill = unibeSaphire()) + -->

<!--   labs(x = "", y = "Laboratory-confirmed cases") + -->

<!--   theme_minimal() -->

<!-- ``` -->

<!-- ## Conclusions -->

<!-- The number of laboratory-confirmed cases of COVID-19 in Switzerland rapidly increased during October 2020 and subsequently declined. -->
